Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-10-22 demystify.tex
updates

Having a strong letter from an internationally recognized researcher will \emph{greatly strengthen} your application. A strong letter from a well-known researcher can outweigh the lack of publications (or low GPA or unknown school).

However, obtaining letters from famous people
can be challenging for international students, who might not have many interactions with such experts. So it is fine to have a letter from people (e.g., profs, researchers, postdocs who mentored you) who know you well enough to talk about \emph{your research experience and capabilities}.

>>>>

\paragraph{LoR from Famous Ppl?} Having a strong letter from an internationally recognized researcher will \emph{greatly strengthen} your application. A strong LOR from such a researcher can outweigh the lack of publications (or low GPA or unknown school).

%However, obtaining letters from famous people
%can be challenging for international students, who might not have many interactions with such experts.

However, let's face it.  Most of us don't have an opportunity to interact or work with well-known researchers.  
So what to do? It is perfectly fine to have a letter from people who know you well enough to talk about \emph{your research experience and capabilities}. These include profs., researchers, postdocs who have mentored and worked with you. In fact, a personal, customized, and strong letter from even a senior PhD grad student who mentors and knows you well is much better than a generic letter from a well-known superstar who does not know you well.

It is also worth noting that a LoR from a ``full'' senior professor who has not been active in research might not be as strong as a LoR from a junior faculty who has been actively mentoring you in research.  This applies to administrative (e.g., chairs, directors, and deans) also (\autoref{sec:admin-letters}.) The fame of the writer is less important than how well they know you and can write about your research ability.
